The vertical Fermi and eROSITA bubbles inclined jets: A proof-of-concept study

### 2021-12-19 paper.tex
update

  \textsc{gamer-sr} adopts a new algorithm \citep{tseng2021} to convert between\
  primitive ($\rho$, $U^{j}$, $p$) and conserved variables ($D$, $M^{j}$, $\tilde{E}$),\
  significantly reducing numerical error caused by catastrophic cancellations\
  that commonly occur within the regions with high Mach number. e.g., jet-ISM interaction zones.

@@

  The initial density profile based on the above construction is shown in \Cref{density-profile}\
  and compared to the observed result beyond 1 kpc \citep{Miller_2013}.\

@@

  A crucial ingredient in our work is the clumpy ISM disk initialized by\
  the publicly available pyFC code
  \footnote{\url{https://pypi.python.org/pypi/pyFC}}.
  The spatial density distribution $\rho(\bold{x})$ of clumpy ISM obeys\
  the log-normal probability distribution in real space,\
  and the Kolmogorov power spectrum in the Fourier space.
  \begin{equation}
    D(k)=\int k^{2} \hat{\rho}(k)\hat{\rho}^{*}(k)dk \propto k^{-5/3},
  \end{equation}
  where $\hat{\rho}(k)$ is the Fourier transform of $\rho(\bold{r})$.

>>>>

  \textsc{gamer-sr} adopts a new algorithm \citep{tseng2021} to convert between\
  primitive ($\rho$, $U^{j}$, $p$) and conserved variables ($D$, $M^{j}$, $\tilde{E}$),\
  significantly reducing numerical error caused by catastrophic cancellations\
  that commonly occur within the regions with high Mach number flows. e.g., jet-ISM interaction zones.

@@

  The initial density profile based on the above construction is shown in \Cref{density-profile}\
  and compared to the observed result \citep{Miller_2013} beyond 1 kpc.\

@@

  A crucial ingredient in our work is the clumpy ISM disk initialized by\
  the publicly available pyFC code
  \footnote{\url{https://pypi.python.org/pypi/pyFC}}.
  The spatial density distribution $\rho(\bold{x})$ of clumpy ISM obeys\
  the log-normal probability distribution in real space,\
  and the Kolmogorov power spectrum in the Fourier space.
  \begin{equation}
    D(k)=\int k^{2} \hat{\rho}(k)\hat{\rho}^{*}(k)dk \propto k^{-5/3},
  \end{equation}
  where $\hat{\rho}(k)$ is the Fourier transform of $\rho(\bold{x})$.
